Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-05-10 Moltres.tex
corrections of some stretched truths in the intro

Molten salt reactor concepts received considerable interest
in the 1950s and 60s with development of the \gls{ARE} and
later the \gls{MSRE} at \gls{ORNL}. With the inclusion of the \gls{MSR} among the
Generation-IV reactor designs, the reactor concept has gained renewed research
interest in the past decade. Some of the advantages offered by the \gls{MSR}
include lower fissile inventories, no radiation damage constraint on attainable
fuel burn-up, no spent nuclear fuel, no requirement to fabricate and handle
solid fuel, and a homogeneous isotopic composition of fuel in the
reactor \cite{noauthor_gen_2008}. These characteristics give the \gls{MSR} a
potentially unique capability for actinide burning and extension of fuel
resources.

\gls{MSR} modeling efforts are focused on description of steady-state and
transient behavior. Krepel et. al. extended the in-house light-water reactor
diffusion code DYN3D to consider drift of delayed neutron precursors alongside
the reactor temperature profile, re-casting the extended code as
DYN3D-MSR \cite{krepel_dyn3d-msr_2007}. DYN3D-MSR was compared against
experimental \gls{MSRE} data and was then used to simulate local fuel channel
blockages as well as local temperature perturbations. In a similar vein, Kophazi
et. al. used iterative coupling between in-house three dimensional neutronic and
one-dimensional heat conduction models DALTON and THERM to analyze the normal
operational state of the \gls{MSRE} and some channel-blocking-incident
transients \cite{kophazi_development_2009}. Additions in the Kophazi model
included entrance effects of heat transfer coefficients as well as thermal
coupling between fuel channels through moderator heat conduction. More recently,
Cammi et. al. performed a 2D-axisymmetric single-channel analysis of the
\gls{MSBR} using the commercial finite element package COMSOL
Multiphysics \cite{cammi_multi-physics_2011}. Advances in this work included
solution of the fuel salt velocity field, use of heterogeneous group constants
in fuel and moderator regions, and employment of a software package (COMSOL)
intrinsically designed for coupled multi-physics simulation.

>>>>

Molten salt reactor concepts garnered considerable interest in the 1950s and 
60s with development of the \gls{ARE} and later the \gls{MSRE} at \gls{ORNL}. 
With the inclusion of the \gls{MSR} among the Generation-IV reactor designs 
\cite{gen_IV}, this reactor concept has gained renewed research interest in the 
past decade, with many new nuclear companies proposing both fluid-fuelled and 
solid-fuelled commerical \gls{MSR} designs 
\cite{terrapower,terrestrial,elysium,thorcon,kairos}. Two key advantages 
offered by the fluid-fuelled \gls{MSR} are improved fuel utilization and no 
radiation damage constraint on attainable fuel burn-up. Together, these 
attributes result in significantly reduced core fissile inventories and spent 
nuclear fuel mass \cite{noauthor_gen_2008}.  These characteristics give the 
\gls{MSR} a potentially unique capability for actinide burning and extension of 
fuel resources.

\gls{MSR} modeling efforts are focused on description of steady-state and
transient behavior. Krepel et. al. extended the in-house \gls{LWR}
diffusion code DYN3D to consider drift of delayed neutron precursors alongside
the reactor temperature profile, re-casting the extended code as
DYN3D-MSR \cite{krepel_dyn3d-msr_2007}. DYN3D-MSR was compared against
experimental \gls{MSRE} data and was then used to simulate local fuel channel
blockages as well as local temperature perturbations. In a similar vein, Kophazi
et. al. used iterative coupling between in-house three-dimensional neutronic and
one-dimensional heat conduction models DALTON and THERM to analyze the normal
operational state of the \gls{MSRE} and some channel-blocking-incident
transients \cite{kophazi_development_2009}. Additions in the Kophazi model
included entrance effects of heat transfer coefficients as well as thermal
coupling between fuel channels through moderator heat conduction. More recently,
Cammi et. al. performed a 2D-axisymmetric single-channel analysis of the
\gls{MSBR} using the commercial finite element package COMSOL
Multiphysics \cite{cammi_multi-physics_2011}. Advances in this work included
solution of the fuel salt velocity field, use of heterogeneous group constants
in fuel and moderator regions, and employment of a software package (COMSOL)
intrinsically designed for coupled multi-physics simulation.
